---
title: "Clustering Coffee Shop Customer Behavior"
author: "Sakib Shahriar"
date: "September 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Necessary Libraries
```{r }
library(TraMineR)
library(cluster)
library(dbscan)
library(clusterCrit)
library(ClusterR)
```


## Read Data and Create State Sequence Object


```{r }
cafeData <- read.csv(file = "User_Sequence_Data.csv", header = TRUE)
head(cafeData,3) #Print first 3 obsercations
dim(cafeData) #Im using 2000 observations here

#Create labels for the sequence object
cafeData.seq.labels <- c("BookShelf", "PS4", "Counter", "Side1", "Side2", "Business", "Corner")
#create a sequence object, the sequence appears from 2-31st column
cafeData.seq <- seqdef(cafeData, var = 2:31, labels = cafeData.seq.labels)
coffeecc <- seqsubm(cafeData.seq, method = "TRATE")

TrueLabels = as.integer(cafeData$Behaviour) #Extract the ground truth labels as integers
```



## Generating the distance matrices


```{r }
#Compute Optimal Matching, Lowest common prefix, Lowest Common Subsequence distance matrix
coffee.OM <- seqdist(cafeData.seq, method = "OM", sm = coffeecc)
coffee.LCP <- seqdist(cafeData.seq, method = "LCP")
coffee.LCS <- seqdist(cafeData.seq, method = "LCS")

```


## Hierarchical clustering using OM


```{r }
clusterward <- agnes(coffee.OM, diss = TRUE, method = "ward")
cluster6.OM <- cutree(clusterward, k = 8) #cluster membership
table(cluster6.OM) #Check cluster assignment


#Internal and External Validation
intCriteria(coffee.OM,as.integer(cluster6.OM),c("Silhouette","Calinski_Harabasz","Dunn")) 
external_validation(TrueLabels, as.integer(cluster6.OM), method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, as.integer(cluster6.OM), method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, as.integer(cluster6.OM), method = "adjusted_rand_index", summary_stats = FALSE)

```



## Hierarchical clustering using LCP


```{r }
clusterward.LCP <- agnes(coffee.LCP, diss = TRUE, method = "ward")
cluster6.LCP <- cutree(clusterward.LCP, k = 8) #cluster membership
table(cluster6.LCP)

#Internal and External Validation
intCriteria(coffee.LCP,as.integer(cluster6.LCP),c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, cluster6.LCP, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, cluster6.LCP, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, cluster6.LCP, method = "adjusted_rand_index", summary_stats = FALSE)

```


## Hierarchical clustering using LCS


```{r }
clusterward.LCS <- agnes(coffee.LCS, diss = TRUE, method = "ward")
cluster6.LCS <- cutree(clusterward.LCS, k = 8) #cluster membership
tbleLCS <- table(cluster6.LCS)

intCriteria(coffee.LCS,as.integer(cluster6.LCS),c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, cluster6.LCS, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, cluster6.LCS, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, cluster6.LCS, method = "adjusted_rand_index", summary_stats = FALSE)

```

## K-Medoids clustering using OM


```{r }
K_Med.OM <- pam(coffee.OM, 8, diss = TRUE)
table(K_Med.OM$clustering)

intCriteria(coffee.OM,K_Med.OM$clustering,c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, K_Med.OM$clustering, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, K_Med.OM$clustering, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, K_Med.OM$clustering, method = "adjusted_rand_index", summary_stats = FALSE)

```

## K-Medoids clustering using LCP


```{r }
K_Med.LCP <- pam(coffee.LCP, 8, diss = TRUE)
table(K_Med.LCP$clustering)

intCriteria(coffee.LCP,K_Med.LCP$clustering,c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, K_Med.LCP$clustering, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, K_Med.LCP$clustering, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, K_Med.LCP$clustering, method = "adjusted_rand_index", summary_stats = FALSE)

```



## K-Medoids clustering using LCS


```{r }
K_Med.LCS <- pam(coffee.LCS, 8, diss = TRUE)
table(K_Med.LCS$clustering)

intCriteria(coffee.LCS,K_Med.LCS$clustering,c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, K_Med.LCS$clustering, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, K_Med.LCS$clustering, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, K_Med.LCS$clustering, method = "adjusted_rand_index", summary_stats = FALSE)

```


## DBSCAN clustering using OM


```{r }
dbscan::kNNdistplot(coffee.OM, k =  15)
db.OM<-dbscan(coffee.OM, MinPts = 15,eps= 240 )
table(db.OM$cluster)

intCriteria(coffee.OM,as.integer(db.OM$cluster),c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, db.OM$cluster, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, db.OM$cluster, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, db.OM$cluster, method = "adjusted_rand_index", summary_stats = FALSE)

```


## DBSCAN clustering using LCP


```{r }
dbscan::kNNdistplot(coffee.LCP, k =  15)
db.LCP<-dbscan(coffee.LCP, MinPts = 15,eps= 89 )
table(db.LCP$cluster)


intCriteria(coffee.LCP,as.integer(db.LCP$cluster),c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, db.LCP$cluster, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, db.LCP$cluster, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, db.LCP$cluster, method = "adjusted_rand_index", summary_stats = FALSE)

```


## DBSCAN clustering using LCS


```{r }
dbscan::kNNdistplot(coffee.LCS, k =  15)
db.LCS<-dbscan(coffee.LCS, MinPts = 15,eps= 250 )
table(db.LCS$cluster)

intCriteria(coffee.LCS,as.integer(db.LCS$cluster),c("Silhouette","Calinski_Harabasz","Dunn"))
external_validation(TrueLabels, db.LCS$cluster, method = "purity", summary_stats = FALSE)
external_validation(TrueLabels, db.LCS$cluster, method = "entropy", summary_stats = FALSE)
external_validation(TrueLabels, db.LCS$cluster, method = "adjusted_rand_index", summary_stats = FALSE)

```
#END